---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# demopkg

<!-- badges: start -->
<!-- badges: end -->

The goal of demopkg is to practice making a package.

## Installation

You can install the development version of demopkg like this:

``` r
devtools::install_github("psyteachr/demopkg")
```


```{r, eval= FALSE}
library(demopkg)
```


### Coding Club

This demo package can be used to allow people to catch up with the [Coding Club](https://psyteachr.github.io/intro-r-pkgs/) sessions. 

To clone this package project to your computer, download the zip file using the green Code button above.

Alternatively, you can run the following code. Set `destdir` to the directory where you want to save this project directory (defaults to your current working directory). 

```{r, eval = FALSE}
# set fork = TRUE if you want to fork to your github 
usethis::create_from_github("psyteachr/demopkg", 
                            destdir = "./",
                            fork = FALSE)
```

The list below shows what is currently included in the package.

1. [Setting up](https://psyteachr.github.io/intro-r-pkgs/01-setup.html): package structure, DESCRIPTION file, license, and README
2. [Adding data](https://psyteachr.github.io/intro-r-pkgs/02-data.html): dataset `self_res_att` included
3. [Custom functions](https://psyteachr.github.io/intro-r-pkgs/03-functions.html): added functions `round0()` and `apa_t_pair()`



